\documentclass[final,3p,times,pdflatex]{elsarticle}
%\usepackage{axodraw}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color} 
\definecolor{Red}{cmyk}{0,1,1,0}
\definecolor{Blue}{cmyk}{1,0.75,0,0}

\newcommand\beq{\begin{eqnarray}}
\newcommand\eeq{\end{eqnarray}}


% beginning of macros
\def\SOFTSUSY{{\tt SOFTSUSY}}
\def\code#1{{\tt #1}}

\journal{Computer Physics Communications}

\begin{document}

\begin{frontmatter}

\begin{flushright}
DAMTP-2017-??\\
\end{flushright}

\title{The Calculation of Sparticle and Higgs Decays in the Minimal and Next-to-Minimal Supersymmetric Standard Models: {\tt SOFTSUSY4.0}}

\author[damtp]{B.C.~Allanach}
\cortext[cor1]{Corresponding author}
\author[damtp]{T.~Cridge}
\ead{T.Cridge@damtp.cam.ac.uk}
\address[damtp]{DAMTP, CMS, University of Cambridge, Wilberforce road,
  Cambridge, CB3  0WA, United Kingdom}
\begin{abstract}
We describe a major extension of the {\tt SOFTSUSY} spectrum calculator to
include 
the calculation of the decays of branching ratios and lifetimes of sparticles
into lighter 
sparticles, covering  the next-to-minimal supersymmetric standard model
(NMSSM) as 
well as the minimal supersymmetric standard model (MSSM).
This document
acts as a manual for the
new version of {\tt SOFTSUSY}, which includes the calculation of sparticle
decays. We collect explicit expressions for the various partial widths in the
appendix. 
\end{abstract}

\begin{keyword}
MSSM, NMSSM, branching ratio, lifetime
\PACS 12.60.Jv
\PACS 14.80.Ly
\end{keyword}
\end{frontmatter}

\section{Program Summary}
\noindent{\em Program title:} \SOFTSUSY{} \\
{\em Program obtainable   from:} {\tt http://softsusy.hepforge.org/} \\
{\em Distribution format:}\/ tar.gz \\
{\em Programming language:} {\tt C++}, {\tt fortran} \\
{\em Computer:}\/ Personal computer. \\
{\em Operating system:}\/ Tested on Linux 4.4.0-36-generic, Linux 3.13.0-93-generic
\\
{\em Word size:}\/ 64 bits. \\
{\em External routines:}\/ None \\
{\em Typical running time:}\/ 0.1-1 seconds per parameter point. \\
{\em Nature of problem:}\/ Calculating supersymmetric particle partial decay
widths in the 
MSSM or the NMSSM\@, given the parameters and spectrum which has already been
calculated by \SOFTSUSY{}. \\
{\em Solution method:}\/ Analytic expressions for tree-level 2 body decays and
one-dimensional numerical integration for 3 body and loop-level decays.\\
{\em Restrictions:} Decays are only calculated in the real $R-$parity conserving
MSSM  or the real $R-$parity conserving
NMSSM only. \\
{\em CPC Classification:}\/ 11.1 and 11.6. \\
{\em Does the new version supersede the previous version?:}\/ Yes. \\
{\em Reasons for the new version:}\/ Significantly extended functionality. The
decay rates and branching ratios of sparticles are particularly useful for
collider searches. Decays calculated in the NMSSM will be a particularly
useful check of the other programs in the literature.\\
{\em Summary of revisions:}\/
Addition of the calculation of sparticle and Higgs decays. 
All 2-body and important 3-body tree-level
decays, including phenomenologically important loop-level decays (notably,
higgs decays to $gg$ and $\gamma \gamma$). Next-to-leading order corrections
are added to higgs 
decays to $q \bar q$ for quarks $q$ of any flavour.

\section{Introduction}
The phenomenology of simple supersymmetric extensions of the Standard Model
has become something of an industry in particle physics of late. The potential
of such models to explain the technical hierarchy problem (i.e.\ the relative
smallness of the Higgs mass as compared to the Planck or gauge unification
scale) has motivated its study. The models have potential implications for
cosmology as well as for collider physics. Several different computationally
tools are necessary for the study of the models'
phenomenology~\cite{Allanach:2008zn}. The initial step is a calculation of the
supersymmetric spectrum, as well as particle couplings. This is the step 
that the computer program \SOFTSUSY~has previously performed, in the
$R-$parity conserving MSSM~\cite{Allanach:2001kg}, the $R-$parity conserving
NMSSM~\cite{Allanach:2013kza} and the $R-$parity violating
MSSM~\cite{Allanach:2009bv}. By adding higher order corrections, the program
has been extended~\cite{Allanach:2011de} to calculate neutrino masses and
mixings in the presence of lepton number violation. Further non-trivial
additions of higher order corrections result in increased precision for the
gauge 
and Yukawa couplings~\cite{Allanach:2014nba} and the squark and gluino pole
masses~\cite{Allanach:2016rxd}. Other publicly available computer programs
exist which perform the task of computing the supersymmetric spectrum: for the
MSSM, there is \code{FLEXIBLESUSY}~\cite{Athron:2014yba}, 
\code{ISASUSY}~\cite{Paige:2003mg}, \code{SUSEFLAV},
\code{SUSPECT}~\cite{Djouadi:2002ze}
and \code{sPHENO}~\cite{Porod:2003um}. In the NMSSM, there is only one
stand-alone dedicated tool for spectrum calculation:
\code{NMSSMTools}~\cite{Ellwanger:2004xm,Ellwanger:2006rn}, whereas the
\code{SARAH}~\cite{Staub:2008uz} framework can be combined with
\code{FLEXIBLESUSY} or \code{sPHENO} in order to calculate the spectrum. 
The plethora of computer programs is useful: some of them use different
approximations and extend to different models. Even the programs having the
same apparent approximations differ in their numerical output because the
higher order corrections not included are implicitly different: both for the
sparticle spectrum~\cite{Allanach:2003jw} and the Higgs
masses~\cite{Allanach:2004rh,Staub:2015aea,deFlorian:2016spz}. Thus, the size of
differences between the programs for observables calculated at the same order
or approximation serve as an rough estimate of the size of higher order
corrections. In some cases, different approximations are used and these can
help elucidate 

In order to provide predictions for future sparticle and higgs searches at
colliders, or indeed in order to interpret searches there in terms 
of the MSSM and NMSSM, a cross-section estimate is required, as well as 
simulations of collisions are required in order to
estimate acceptances and efficiencies. For simulations, estimates of the
various decay partial widths for the sparticles and Higgs
particles are required. Some Monte-Carlo event generators perform this task in
the MSSM, for example \code{PYTHIA}~\cite{Sjostrand:2014zea} or
\code{HERWIG7}~\cite{Bahr:2008pv}, but 
there also exist dedicated tools like
\code{SUSYHIT}~\cite{Djouadi:2006bz} or \code{HDECAY}~\cite{Djouadi:1997yw} and
\code{FeynHiggs}~\cite{Heinemeyer:1998yj} (the latter two
specialising in the 
Higgs boson decays). \code{sPHENO}~also contains a decay
calculation for the MSSM. In the NMSSM however, the options for calculating
sparticle and 
Higgs decays are rather slim: \code{NMSSMTools}~being the only stand-alone
option. Previous versions of \code{SOFTSUSY}~contained an interface to
\code{NMSSMTools}~so that the NMSSM spectrum and couplings could then be fed
into the program in order to predict sparticle and Higgs boson partial decay
widths. 

The present paper describes a significant extension in functionality in
\code{SOFTSUSY}: to calculate and output the various partial widths for the
decays of sparticles and Higgs bosons in the MSSM and in the NMSSM. 
Emphasis has been placed on speed of execution, preferring to perform as much
of the calculation analytically as is practicable. 
We hope
that this addition of functionality to \code{SOFTSUSY}~will facilitate
collider studies of sparticle and supersymmetric 
Higgs searches: both through the study of differences with the other programs
as an estimate of the size of theoretical uncertainty in the prediction, and 
through a fast and unified computation. 

The rest of the paper is organised as follows: in Section~\ref{sec:conv}, we 
specify the conventions used in this paper and give some details about the
method of computation. Next, in section~\ref{sec:comp}, we provide a few
examples of comparison tests 
with a couple of other publicly available tools for the MSSM and the NMSSM,
before summing up in Section~\ref{sec:sum}. We show how to run the program and
provide explicit flags for controlling its behaviour in
Appendix~\ref{sec:run}, providing some sample output in
Appendix~\ref{sec:out}. 
We provide explicit formulae for
the partial widths in Appendix~\ref{sec:exp}: these have not been collected
together in one reference before. 

\subsection{Conventions and Method \label{sec:conv}}
{\em Tom: Please set up conventions for use later in the appendix. You can use
any specified in the other SOFTSUSY manuals, provided you explicitly refer to
them, saying that's what you're using.}

For two body decay modes, partial widths are explicitly coded in order to
provide fast evaluation. For three body decay modes, the phase space integral
has been reduced to a one-dimensional integral analytically, which is then
performed using adaptive Gaussian numerical integration~\cite{numRec}.



\section{Comparison with SUSYHIT and NMSSMTools \label{sec:comp}}

We performed specific and fairly extensive tests for particular benchmark
points with \code{sPHENO} and ~\code{SUSYHIT}. {\em Tom, please describe here
  something about how these tests were performed, stating the level of
  agreement etc}.

{\em Tom: then, we want a few example results to show, I guess.}

\section{Summary \label{sec:sum}}
The fast automated computation of the spectrum and decays of particles in the
MSSM and the NMSSM is now possible all within \code{SOFTSUSY}, and they are
necessary steps in the simulation of collider signatures, required for both
the prediction and interpretation of the collider signatures. The inclusion
of sparticle and Higgs decay partial widths and should aid in estimating 
theoretical uncertainties, particularly in regard to decays in the NMSSM,
where there are few other publicly available tools. 
\code{SOFTSUSY}~has been routinely used by the ATLAS and CMS experiments to
interpret their searches for supersymmetric particles, and so having the
decays calculated within the same package as the spectrum should be easier. 
The usual SLHA and SLHA2
conventions for input and output have been followed in order to facilitate
`joining up' \code{SOFTSUSY}~with other observable calculating programs in a
bug-free manner, for example programs that perform Monte-Carlo event
simulation. 

\section*{Acknowledgments}
This work has been partially supported by STFC HEP Consolidated grant 
ST/L000385/1. We thank the Cambridge SUSY working group for helpful
discussions. 

\appendix

\section{Running \SOFTSUSY~to Calculate Sparticle Decays  
\label{sec:run}}

\SOFTSUSY~produces an executable called \code{softpoint.x}. It can be run by
the command
\begin{verbatim}
./softpoint.x leshouches < inOutFiles/lesHouchesInput
\end{verbatim}
where the file \code{inOutFiles/lesHouchesInput}~contains an ASCII file
for input
prepared in SUSY Les Houches Accord (SLHA)~\cite{Skands:2003cj} or
SLHA2~\cite{Allanach:2008qq} format. 
A \code{SOFTSUSY}-specific \code{Block}~of the SLHA input file is provided in
the case that decays are required:
\begin{verbatim}
Block SOFTSUSY               # Optional SOFTSUSY-specific parameters
    0   1.000000000e+00      # Calculate decays in output (only for RPC (N)MSSM)
\end{verbatim}
If this block is absent, or if the numerical value is instead
\code{0.000000000e+00}, then decays will not be calculated. 
Other input options are available for changing the behaviour of the program as
regards sparticle decays:
\begin{verbatim}
Block SOFTSUSY               # Optional SOFTSUSY-specific parameters
   24   1.000000000e-06      # If decay BR is below this number, don't output
   25   1.000000000e+00	     # If set to 0, don't calculate 3-body decays (1=default)
\end{verbatim}
Thus, parameter \code{24}~under this block sets the smallest decay branching
ratio that will be output (the default is, as listed, $10^{-6}$) whereas 
parameter \code{25}~can be used to instruct \code{SOFTSUSY}~not to calculate
the 3-body modes, which are more computationally intensive, requiring
numerical integration. 

If command-line input is required (see
Refs.~\cite{Allanach:2001kg,Allanach:2013kza} 
for a full description), the user can use the argument 
\code{--decays}~to tell \SOFTSUSY~to perform the decay calculation. 
The command line argument \code{--minBR=<value>}~tells SOFTSUSY which minimum
branching ratio to print out in each decay table (where \code{<value>} is
replaced by a numerical value between \code{0}~and \code{1}), whereas the
command line argument \code{--dontCalculateThreeBody}~tells SOFTSUSY {\em
  not}\/ to calculate the 3-body decays of sparticles in order to save time. 

\section{Sample Output \label{sec:out}}
The output comes in the standard SLHA/SLHA2
format~\cite{Skands:2003cj,Allanach:2008qq}. A sample of the part relevant for
decays is shown here:
{\small
\begin{verbatim}
#     PDG         Width             
DECAY 1000021     1.93499813e+01   # gluino decays
#     PW                BR                NDA      PDG1        PDG2        PDG3       
      3.02052144e-01    1.56099450e-02      2     1          -1000001     0         # ~g -> d ~d_L*
      3.02052144e-01    1.56099450e-02      2    -1           1000001     0         # ~g -> db ~d_L
      6.40860115e-01    3.31194178e-02      2     1          -2000001     0         # ~g -> d ~d_R*
      6.40860115e-01    3.31194178e-02      2    -1           2000001     0         # ~g -> db ~d_R
      3.20263354e-01    1.65510937e-02      2     2          -1000002     0         # ~g -> u ~u_L*
      3.20263354e-01    1.65510937e-02      2    -2           1000002     0         # ~g -> ub ~u_L
      6.11876735e-01    3.16215672e-02      2     2          -2000002     0         # ~g -> u ~u_R*
      6.11876735e-01    3.16215672e-02      2    -2           2000002     0         # ~g -> ub ~u_R
      3.02068273e-01    1.56107786e-02      2     3          -1000003     0         # ~g -> s ~s_L*
      3.02068273e-01    1.56107786e-02      2    -3           1000003     0         # ~g -> sb ~s_L
      6.40883736e-01    3.31206386e-02      2     3          -2000003     0         # ~g -> s ~s_R*
      6.40883736e-01    3.31206386e-02      2    -3           2000003     0         # ~g -> sb ~s_R
      3.20253636e-01    1.65505915e-02      2     4          -1000004     0         # ~g -> c ~c_L*
      3.20253636e-01    1.65505915e-02      2    -4           1000004     0         # ~g -> cb ~c_L
      6.11875992e-01    3.16215288e-02      2     4          -2000004     0         # ~g -> c ~c_R*
      6.11875992e-01    3.16215288e-02      2    -4           2000004     0         # ~g -> cb ~c_R
      1.04760821e+00    5.41400117e-02      2     5          -1000005     0         # ~g -> b ~b_1*
      1.04760821e+00    5.41400117e-02      2    -5           1000005     0         # ~g -> bb ~b_1
      6.79062885e-01    3.50937231e-02      2     5          -2000005     0         # ~g -> b ~b_2*
      6.79062885e-01    3.50937231e-02      2    -5           2000005     0         # ~g -> bb ~b_2
      4.19818556e+00    2.16960704e-01      2     6          -1000006     0         # ~g -> t ~t_1*
      4.19818556e+00    2.16960704e-01      2    -6           1000006     0         # ~g -> tb ~t_1
[ ... ]
\end{verbatim}}
In concordance with SLHA conventions, the widths/partial widths
(\code{PW}) are output 
in units 
of GeV. \code{NDA}~lists the number of daughter particles and
\code{PDGi}~lists the
Particle Data Group~(PDG) code of daughter \code{i} (Section 43 of
Ref.~\cite{Olive:2016xmw}). 
The comment at the end of each line after \code{\#}~lists the decay
mode for easy perusal by the eye.
\section{Explicit Expressions Used For Partial Widths \label{sec:exp}}



\bibliography{decays}
\bibliographystyle{elsarticle-num}
\end{document}
